\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2016-11-24 doc/publications/plos16/plos16.tex
Add missing time

\multirow{3}{*}{phase1\_chr22: 1,092 x 490,036} & \cursedforest\ & 0.04  & 1 min 50 seconds                        \\
                                                & RF - Spark ML  &  Aidan           &           Aidan         \\
                                                & RF - R         & 0.05       & 24 min           \\
                                                & ranger - R      & 0.06       & 1 min 10 seconds       \\
                                                & ranger - c++     & 0.06       & 7 mins            \\

>>>>

\multirow{3}{*}{phase1\_chr22: 1,092 x 490,036} & \cursedforest\ & 0.04  & 1 min 50 seconds                        \\
                                                & RF - Spark ML  &  0.05           &           7 min 44 seconds         \\
                                                & RF - R         & 0.05       & 24 min           \\
                                                & ranger - R      & 0.06       & 1 min 10 seconds       \\
                                                & ranger - c++     & 0.06       & 7 min            \\
